---
title: "theCLT"
author: "Dr. J"
date: '2022-03-29'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")
my1000 <- sample(Homers_data$kkardashtemp ,size = 1000, replace=T)
densityplot(my1000,main="original data")

```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

This is  a bimodal plot- i.e. two peaks.  The peaks appear to be the same size

Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size?   

 The resulting plot is tri-modal.  Middle peak is higher than those on either side.  The side peaks appear to be the same height.   

Do this again for 4 random samples  

```{r}
numb = 4
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
```
Now there appears to be 5 modes!  Decreasing in size from the center mode  


Then again for 9 random samples

```{r}
numb = 9
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
```


this is starting to look unimodal!  

then 16 random samples

```{r}
numb = 16
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
```

more like the normal curve  

finally for 36 random samples.

```{r}
numb = 36
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")
```

definitely unimodal!  

Write a summary paragraph describing what you observed and how it relates to the central limit theorem.

Be sure to comment on both the mean and standard deviation of the sample averages - the CLT makes a statement about what to expect from both.

The more samples used, the closer this becomes to the normal distribution.   The mean remains around 50, but the standard deviation is decreasing!

with 9 samples the data range is 10-90 SD ~ 20  
with 16 samples data range is 20-80  SD ~ 15  
with 36 samples data range is 30-70.  SD ~ 10  
 

Then submit the link to your github project  to canvas to complete this assignment.